\subsection{Liveliness Generation}
Liveliness is a determination of usage of the symbols. A symbol $x$ is live at statement $s$ if
\begin{enumerate}
  \item There exists a statement $s'$ that uses $s$.
  \item There is a path from $s$ to $s'$ in the CFG.
  \item From $s$ to $s'$, there is no re-assignment of $x$.
\end{enumerate}
We compute liveliness by passing live information through adjacent statements through a function
$$L(s,x, \text{in | out}).$$
This function determines whether a symbol $x$ is live incoming or outcoming of a statement $s$. We follow these rules:
\begin{enumerate}
  \item If a condition $C$ uses $x$, then $x$ is live incoming this assignment.
        \begin{equation}
          L(C(x), x, \mathrm{in}) = \mathrm{True}.
        \end{equation}
  \item If an assignment uses $x$ on the right-hand side, then $x$ is live incoming this assignment.
        \begin{equation}
          L(\ldots := \mathrm{LHS}(x), x, \mathrm{in}) = \mathrm{True}.
        \end{equation}
  \item If an assignment refers to $x$ on the left-hand side but not the right-hand side, then $x$ is not live incoming this assignment
        \begin{equation}
          L(x := e, x, \mathrm{in}) = \mathrm{False}.
        \end{equation}
  \item If a statement does not refer to $x$, then the liveliness of $x$ does not change when outcoming the statement.
        \begin{equation}
          L(s, x, \mathrm{in}) = L(s, x, \mathrm{out})
        \end{equation}
  \item If $x$ is live incoming a statement $s'$, then $x$ is live outcoming predecessors of $s'$.
        \begin{equation}
          L(s, x, \mathrm{out}) = \bigvee \left\{ L(s',x,\mathrm{in}) : s' \text{ is a successor of }  s\right\}.
        \end{equation}
\end{enumerate}

The first three rules are run once. Then the last two rules are run iteratively until no changes appear on the liveliness dictionary. Live symbols at each statement \texttt{stmt} is computed as all live symbols outcoming of this statement and incoming of its successor.

\begin{lstlisting}[language = python, caption={Liveliness generator context}, label={listing:live-gen-context}]
  class LiveGenContext:
    def __init__(self, 
                  stmt,            # current visited statement
                  refered_symbols  # current refered symbols
                ):
    # Initialization
\end{lstlisting}
